Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-02 manuscript.tex
20160701
20160702

u_1 = -\frac{\bar\delta\bar\rho\eta_1(t)sgn(\bar S)+k_1\bar S}{\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)}\\
u_2 = -\frac{\bar\delta\bar\rho\eta_2(t)sgn(\bar S)+k_2\bar S}{\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)}.

@@

@@

In this simulation, the three-satellite inline tethered system maintains rotating at angular rate $\omega_0=0.25$ in initial stage, and meanwhile, the initial individual angle, $\phi_0 = 0.2$, means that the individual system has been swung to a undesired attitude. The MHSM scheme aims to regulate the system to a desired attitude in the specified condition, and in particular the desired conditions are as follows, $\omega_d = 0.25$, $\phi_d = 0$ and $\dot{\phi}_d = 0$. In final stage, the entire system will keep rotating, and meanwhile three individual satellites are nonskew and in a line consequently.\par
Use MHSM scheme to regulate the individual system shown as Eq.~(\ref{eq:individualsys}), and the guidance situation of sliding mode is illustrated in Figure~\ref{Figure:sm} where $s_1$ and $s_2$ converge asymptotically as well as $S$. It is the trajectory of $s_1$ that nearly overlaps with the one of $S$, and $s_2$ fluctuates slightly in a certain neighbour region around the origin. Paying attention on validating the convergence of each sliding mode, it is obvious that $S$, $s_1$ and $s_2$ reach the neighbour region around the origin at about $2s$ and stay stable. Incidentally, the state of the angle and the torque are both physical meaningful.\par
The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about $2s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$, so does the array angular rate.\par
The characteristics of the input saturation are exhibited in Figure~\ref{Figure:Torque}, and the existence of the input bound makes the curves not smooth any more. In particular, it cuts off the oversize input signal to be a bounded value, and resume the regular input once the control signal is located in the region $[T_n,T_p]$. The bound of the input is decided by the physical property of the flywheel equipped in the satellite, and the boundary value is $0.207Nm$ bidirectionally in this section. In Figure~\ref{Figure:Torque}, the saturation occurs at about $0.35s$ and $0.57s$, which is zoomed out for examining more details, and the torque keeps a low-amplitude fluctuation in the neighbour region of the origin after $2s$. That means that the torque utilized to make the system stable, still performs accurately, although the stability of the attitude dynamics for the individual satellite has achieved macroscopically. It is also easy to find that the perturbations don't introduce distinct contaminations into the control system, in another word, the anti-interference ability of the proposed scheme is excellent.

@@

The performance of the attitude regulation can be viewed from Figure~\ref{Figure:2attitude}. It shows that the angular rate of the entire system is stable at the desired rate $\dot\theta=0.25$, and meanwhile, the attitude of the participating satellites is adjusted to the desired status at about $1.8s$. Figure~~\ref{Figure:2s} illustrates the guidance situation of the sliding mode, which indicates that $\sigma_i,i=1,2,3$ and $\bar S$ all converge as desired, and then stay in the neighbour region of the origin in the subsequent time. It is noted that the first-level sliding surfaces are stable in the same time, and obviously this phenomenon proceeds to verify Theorem~\ref{theorem:3}. Figure~\ref{Figure:2u1u2} exhibits the torques of the flywheels equipped in the participating satellites. According to the saturation characteristics of actuators, there exists the bounds of the inputs in the positive and negative direction, and the bounded inputs can be found at about $0.1s$ in this figure.

>>>>

u_1 &= -\frac{\bar\delta\bar\rho\eta_1(t)sgn(\bar S)+k_1\bar S}{\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)}\\
u_2 &= -\frac{\bar\delta\bar\rho\eta_2(t)sgn(\bar S)+k_2\bar S}{\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)}.

@@

In addition, if the inputs are selected as:
u_1 &= -\frac{\bar\delta\bar\rho\eta_1(t)sgn(\bar S)+k_1\bar S_1}{\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)}\\
u_2 &= -\frac{\bar\delta\bar\rho\eta_2(t)sgn(\bar S)+k_2\bar S_2}{\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)}.
\end{split}\label{eq:modified_u1u2}
where $k_1\bar S_1+k_2\bar S_2=k_0\bar S$ with $k_0>0$, one can also obtain the result above.

@@

In this simulation, the three-satellite inline tethered system maintains rotating at angular rate $\omega_0=0.25$ in initial stage, and meanwhile, the initial individual angle, $\phi_0 = 0.2$, means that the individual system has been swung to \begin{color}{red}an\end{color} undesired attitude. The MHSM scheme aims to regulate the system to the specified attitude, and in particular the desired conditions are as follows, $\omega_d = 0.25$, $\phi_d = 0$ and $\dot{\phi}_d = 0$. In final stage, the entire system will keep rotating, and meanwhile three individual satellites are nonskew and in a line consequently.\par
Use MHSM scheme to regulate the individual system shown as Eq.~(\ref{eq:individualsys}), and the guidance situation of sliding mode is illustrated in Figure~\ref{Figure:sm} where $s_1$ and $s_2$ converge to origins as well as $S$. It is the trajectory of $s_1$ that nearly overlaps with the one of $S$, and $s_2$ fluctuates slightly in a certain neighbour region around the origin. Paying attention on the convergence of each sliding mode, it is obvious that $S$, $s_1$ and $s_2$ reach the neighbour region around the origin at about 1.2 $s$ and stay stable. Incidentally, the state of the angle and the torque are both physical meaningful.\par
The situation of the attitude regulation is illustrated in Figure~\ref{Figure:attitude}, in which the array angular rate is adjusted to be the desired value from the initial condition so that the individual satellites and the central satellite are rotating together at the same velocity. It is at about 1.2 $s$ when the trajectory of the attitude angle converges to the preset value, $\phi_d = 0$, so does the array angular rate. \begin{color}{red}The performance of the decentralized control reported in~\cite{chung2008propellant1} is also illustrated in Figure~\ref{Figure:attitude}. In~\cite{chung2008propellant1}, a pair of thrusters are used to dump the angular momentum caused by the saturation of the flywheel speed, and for reducing the consumption of thruster firing, a little gain design is demanded in the decentralized control strategy. Hence, the decentralized control inevitably leads to a slow smooth attitude regulation shown in Figure~\ref{Figure:attitude}. Compared with the the decentralized control scheme, one can find that the MHSM control demonstrates a fast regulation, and although the amplitudes of the varying attitude angle and the array angular rate of the MHSM control are greater with the variations falling in $[-0.05,0.2]$ $rad$ and $[0.225,0.375]$ $rad/s$, respectively, this variations are tolerable in some fast attitude scenarios of the TSS~\cite{Williams2009745}. Even the input saturation occurs during the attitude regulation, the MHSM control scheme guarantees the stability of the system, and hence the selection of the gain is flexible so that the performance of the control system can be adjusted by the suitable parameters. \end{color}\par
The characteristics of the input saturation are exhibited in Figure~\ref{Figure:Torque}, and the existence of the input bound makes the curves not smooth any more. In particular, it cuts off the oversize input signal to be a bounded value, and resume the regular input once the control signal is located in the region $[T_n,T_p]$. The boundary of the input is decided by the physical property of the flywheel equipped in the satellite, and the boundary value is $0.207Nm$ bidirectionally in this section. In Figure~\ref{Figure:Torque}, the saturation occurs from about $0s$ to $0.6s$, which is zoomed out for examining more details, and the torque keeps a low-amplitude fluctuation in the neighbour region of the origin after 1.2 $s$. That means that the torque utilized to make the system stable, still performs accurately, although the stability of the attitude dynamics for the individual satellite has achieved macroscopically. It is also easy to find that the perturbations don't introduce distinct contaminations into the control system, in another word, the anti-interference ability of the proposed scheme is excellent.

@@

The performance of the attitude regulation can be seen from Figure~\ref{Figure:2attitude}. \begin{color}{red}It shows that the angular rate of the entire system is stable at 1.2 $s$, and meanwhile, the attitude of the participating satellites is adjusted to the desired status. Compared with the decentralized control strategy, similar to the case of the three-satellite system, the MHSM control performs the fast regulation with reasonable amplitudes of attitude angle and array angular rate.\end{color} Figure~\ref{Figure:2s} illustrates the guidance situation of the sliding mode, which indicates that $\sigma_i,i=1,2,3$ and $\bar S$ all converge as desired, and then stay in the neighbour region of the origin in the subsequent time. It is noted that the first-level sliding surfaces are stable in the same time, and obviously this phenomenon proceeds to verify Theorem~\ref{theorem:3}. Figure~\ref{Figure:2u1u2} exhibits the torques of the flywheels equipped in the participating satellites. According to the saturation characteristics of actuators, there exists the bounds of the inputs in the positive and negative direction, and the bounded inputs can be found at about $0.1s$ in this figure.
